### 2020-05-31 report/sections/evalconcl/eval/benchmarks.tex
Report: complete benchmarks
Report: proofread some benchmark

Whilst web applications that implement our generated APIs enjoy
communication safety guarantees, the presence of the session runtime acts
as an additional layer of abstraction between the application logic and the
WebSocket transport, which is likely to present a performance trade-off.

@@

To measure the overhead of our implementation, we compare the
execution time of an interactive web application implementing the
Ping Pong protocol (\cref{lst:pingpong}) using our generated APIs,
against implementations of the protocol \textit{without} session types.

@@

We note that the Ping Pong protocol implements a \textit{binary} session. 
It would be interesting to observe the overhead in a \textit{multiparty}
context, but due to limited time constraints, we were unable to 
extend our benchmarking suite to support multiple browser targets.
Benchmarking multiparty protocols would also require writing multiple
distinct React applications using the generated APIs -- as this is currently
a manual process, doing this for multiple roles requires more time than
available.

@@

@@

\begin{figure}[!ht]
\captionof{figure}{User interface of Ping Pong \trole{Client}}
\label{fig:pingpongclient}
\end{figure}

>>>>

Whilst web applications implementing our generated APIs enjoy
communication safety guarantees, the presence of the session runtime acts
as an additional layer of abstraction between the application logic and the
WebSocket transport, which is likely to present a performance trade-off.

@@

To measure the overhead of our implementation, we compare the
execution time of web-based implementations of the
Ping Pong protocol (\cref{lst:pingpong}) with and without
our generated APIs.

@@

We note that the Ping Pong protocol implements a \textit{binary} session. 
It would be interesting to observe the overhead in a \textit{multiparty}
context, but due to limited time constraints,
our benchmarking suite does not support multiple browser targets.
Benchmarking multiparty protocols would also require writing multiple
distinct React applications using the generated APIs -- as this is currently
a manual process, doing this for multiple roles requires more time than
available.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{pingpongclient}
\captionof{figure}{User interface of Ping Pong \trole{Client}}
\label{fig:pingpongclient}
\end{figure}

@@
